Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
shortened sentence

                                \textit{Amaya} is a desktop Web editor application (to create and update documents) as well as a lightweight browser that was (1993) developed by W3C to provide a framework to test its technologies.

>>>>

                                \textit{Amaya} is a desktop Web editor application (to create and update documents) as well as a lightweight browser developed by W3C to test its technologies.
